Stabilization-Free Virtual Element Methods

### 2023-06-18 stabfreevem_sinum.tex
revise the paper based on the reports

% REQUIRED
\begin{abstract}
Stabilization-free virtual element methods (VEMs) in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these stabilization-free VEMs. Numerical experiments are provided to test the stabilization-free VEMs.
\end{abstract}

% REQUIRED
\begin{keywords}
virtual element, stabilization-free, macro finite element, norm equivalence, error analysis
\end{keywords}

@@

\section{Introduction}
A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems. The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon. 
Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.

The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.

The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

@@

By the aid of the projector $Q_{K,k}^{\div}$, we advance a stabilization-free nonconforming VEM in arbitrary dimension and a stabilization-free conforming VEM in two dimensions  for second order elliptic problems.
Indeed, these stabilization-free VEMs can be equivalently recast as
primal mixed VEMs.
We prove the norm equivalence \eqref{intro:gradVknormequiv} and the well-posedness of these stabilization-free VEMs, and derive the optimal error estimates. Numerical experiments are provided to test these VEMs.

The idea on constructing stabilization-free VEMs in this paper is simple,
and can be extended to more VEMs and more partial differential equations.

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A stabilization-free nonconforming VEM in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a stabilization-free conforming VEM in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\section{Stabilization-free nonconforming virtual element method}\label{sec:stabfreencfmvem}

@@

In this section we will develop a stabilization-free nonconforming VEM for the second order elliptic problem in arbitrary dimension
\begin{equation}\label{eq:ellipitc2ndproblem}
\begin{cases}
-\Delta u + \alpha u=f & \textrm{ in } \Omega,\\
\qquad\qquad u=0&\textrm{ on } \partial\Omega,
\end{cases}
\end{equation}
where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a nonnegative constant. The weak formulation of problem \eqref{eq:ellipitc2ndproblem} is to find $u\in H_0^1(\Omega)$ such that
\begin{equation}\label{eq:ellipitc2ndproblemweakform}
a(u,v)=(f,v)\quad\forall~v\in H_0^1(\Omega),
\end{equation}
where the bilinear form $a(u, v):=(\nabla_h u, \nabla_h v)+\alpha(u,v)$ with $\nabla_h$ being the piecewise counterpart of $\nabla$ with respect to $\mathcal T_h$.

@@

\subsection{Local inf-sup condition and norm equivalence}
With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design stabilization-free virtual element methods. 
% Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
\begin{lemma}\label{lem:gradVknormequivalence}
It holds the inf-sup condition
\begin{equation}\label{eq:localdiscreteinfsup}    
\|\nabla v\|_{0,K}\lesssim \sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K).
\end{equation}
Consequently,
\begin{equation}\label{eq:gradVknormequivalence}  
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
\end{equation}
\end{lemma}
\begin{proof}
Clearly the norm equivalence \eqref{eq:gradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:localdiscreteinfsup}. We will focus on the proof of \eqref{eq:localdiscreteinfsup}.
Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
\begin{align*}
(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F&=h_K^{-1}(v, q)_F  \quad\quad\,\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \\
(\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \\
(\boldsymbol{\phi}, \boldsymbol{q})_K&=0  \qquad\qquad\qquad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K). 
\end{align*}
Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$. Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$. Apply the integration by parts and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$ to get
\begin{align*}
(\boldsymbol{\phi}, \nabla v)_K&=-(\div\boldsymbol{\phi}, v)_K + (\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K} \\
&=-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K+\sum_{F\in\mathcal F(K)}(\boldsymbol{\phi}\cdot\boldsymbol{n}, Q_{k-1}^Fv)_{F} \\
&=h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2.
\end{align*}
By the norm equivalence \eqref{eq:Vknormequivalence}, we get
\begin{equation}\label{eq:20220204}
\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2= (\boldsymbol{\phi}, \nabla v)_K.
\end{equation}

@@

\subsection{Discrete method}
Define the global nonconforming virtual element space
\begin{align*}
V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
\end{align*}
We have the discrete Poincar\'e inequality \cite{Brenner2003}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
\begin{equation}\label{eq:vempoincareineqlty}
\|v_h\|_0\lesssim |v_h|_{1,h} \quad\forall~v_h\in V_h.
\end{equation}
Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
% Introduce discrete spaces
% \begin{align*}
% \mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
% \mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
% \end{align*}
% with non-negative integer $l$.
% For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_h^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:vem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation}
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
\]

@@

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a stabilization-free virtual element method for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:cfmvem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation} 
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
\]
The stabilization-free VEM \eqref{eq:cfmvem} is uni-solvent.

>>>>

% REQUIRED
\begin{abstract}
Virtual element methods (VEMs) \XH{without extrinsic stabilization} in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these VEMs. Numerical experiments are provided to test the VEMs \XH{without extrinsic stabilization}.
\end{abstract}

% REQUIRED
\begin{keywords}
virtual element, stabilization, macro finite element, norm equivalence, error analysis
\end{keywords}

@@

\section{Introduction}
An additional stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form~\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}.
% , while the stabilization term also brings about some problems. 
The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
% The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization term dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
\XH{
In short, the stabilization term has to be chosen carefully for different partial differential equations to make the VEM work well, which is arduous and reduces its practicality.}

% Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon. 
% Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
% The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}.

% The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
% the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
We intend to construct VEMs \XH{without extrinsic stabilization} in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
The key to construct VEMs \XH{without extrinsic stabilization} is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
\XH{To remove the additional stabilization term, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.}
% $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
% Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

@@

By the aid of the projector $Q_{K,k}^{\div}$, we advance a nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension and a conforming VEM \XH{without extrinsic stabilization} in two dimensions  for second order elliptic problems.
Indeed, these VEMs can be equivalently recast as
primal mixed VEMs.
We prove the norm equivalence~\eqref{intro:gradVknormequiv} and the well-posedness of the VEMs \XH{without extrinsic stabilization}, and derive the optimal error estimates.

\XH{Numerical experiments are provided to test the convergence rate, the invertibility of the local stiffness matrices, the assembling time and the condition number of stiffness
matrix for the VEMs without extrinsic stabilization, which appear competitive with respect to other existing VEMs.}

The idea on constructing VEMs \XH{without extrinsic stabilization} in this paper is simple,
and can be extended to more VEMs and more partial differential equations.
\XH{Since there is no additional stabilization term, these VEMs will be preferred in the engineering community. More benefits of the VEMs without extrinsic stabilization will be the study of future works.}
By the way, we refer to \cite{CicuttinErnLemaire2019} for a hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for weak Galerkin finite element methods \XH{without extrinsic stabilization}.

The rest of this paper is organized as follows. Notation and mesh conditions are presented in Section~\ref{sec:prelim}. 
In Section~\ref{sec:divmacrofem}, $H(\div)$-conforming macro finite elements in arbitrary dimension are constructed. A nonconforming VEM \XH{without extrinsic stabilization} in arbitrary dimension is developed in Section \ref{sec:stabfreencfmvem}, and a conforming VEM \XH{without extrinsic stabilization} in two dimensions is devised in Section \ref{sec:stabfreecfmvem}.
Some numerical results are shown in Section \ref{sec:numericalexamps}.

@@

\section{Nonconforming virtual element method \XH{without extrinsic stabilization}}\label{sec:stabfreencfmvem}

@@

In this section we will develop a nonconforming VEM \XH{without extrinsic stabilization} for the second order elliptic problem in arbitrary dimension
\begin{equation}\label{eq:ellipitc2ndproblem}
\begin{cases}
-\Delta u + \alpha u=f & \textrm{ in } \Omega,\\
\qquad\qquad u=0&\textrm{ on } \partial\Omega,
\end{cases}
\end{equation}
where $\Omega\subseteq\mathbb R^d$ is a bounded polygon, $f\in L^2(\Omega)$ and $\alpha$ is a nonnegative constant. The weak formulation of problem \eqref{eq:ellipitc2ndproblem} is to find $u\in H_0^1(\Omega)$ such that
\begin{equation}\label{eq:ellipitc2ndproblemweakform}
a(u,v)=(f,v)\quad\forall~v\in H_0^1(\Omega),
\end{equation}
where the bilinear form $a(u, v):=(\nabla_h u, \nabla_h v)+\alpha(u,v)$ with $\nabla_h$ being the piecewise counterpart of $\nabla$ with respect to $\mathcal T_h$.

@@

\subsection{Local inf-sup condition and norm equivalence}
With the help of the macro element space $\mathbb{V}_{k-1}^{\rm div}(K)$, we will present a norm equivalence for space $\nabla V_k(K)$, which is vitally important to design virtual element methods \XH{without extrinsic stabilization}. 
% Let $Q_K^{\div}$ be the $L^2$-orthogonal projection operator onto $\mathbb{V}_{k-1}^{\rm div}(K)$ with respect to the inner product $(\cdot, \cdot)_K$.
\begin{lemma}\label{lem:gradVknormequivalence}
It holds the inf-sup condition
\begin{equation}\label{eq:localdiscreteinfsup}    
\|\nabla v\|_{0,K}\XH{\leq C_e}\sup_{\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{\|\boldsymbol{\phi}\|_{0,K}} \quad \forall~v\in V_k(K),
\end{equation}
\XH{where the constant $C_e\geq1$ is independent of the mesh size $h_K$, but depends on the chunkiness parameter of the polytope, the degree of polynomials $k$, the dimension of space $d$, and the shape regularity and quasi-uniform constants of the virtual triangulation $\mathcal T^*_h$.}
Consequently,
\begin{equation}\label{eq:gradVknormequivalence}  
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
\end{equation}
\end{lemma}
\begin{proof}
Clearly the norm equivalence \eqref{eq:gradVknormequivalence} follows from the local inf-sup condition~\eqref{eq:localdiscreteinfsup}. We will focus on the proof of \eqref{eq:localdiscreteinfsup}.
Without loss of generality, assume $v\in V_k(K)\cap L_0^2(K)$.
Based on DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3}, take $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$ such that
\begin{align*}
(\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F&=h_K^{-1}(v, q)_F  \quad\quad\,\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \\
(\div\boldsymbol{\phi}, q)_K&=-h_K^{-2}(v, q)_K  \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \\
(\boldsymbol{\phi}, \boldsymbol{q})_K&=0  \qquad\qquad\qquad\forall~\boldsymbol{q}\in \div\skw\mathring{\boldsymbol{V}}_{k}^{d-2}(K). 
\end{align*}
Then $(\boldsymbol{\phi}\cdot\boldsymbol{n})|_{F}=h_K^{-1}Q_{k-1}^Fv$ for $F\in\mathcal F(K)$. Since $\div\boldsymbol{\phi}\in \mathbb P_{\max\{k-2,0\}}(K)$, we have $\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi})=-h_K^{-2}Q_{k-2}^Kv$. Apply the integration by parts and the fact $v=v-Q_{0}^Kv\in L_0^2(K)$ to get
\begin{align*}
(\boldsymbol{\phi}, \nabla v)_K&=-(\div\boldsymbol{\phi}, v)_K + (\boldsymbol{\phi}\cdot\boldsymbol{n}, v)_{\partial K} \\
&=-(\div\boldsymbol{\phi}-Q_{0}^K(\div\boldsymbol{\phi}), v)_K+\sum_{F\in\mathcal F(K)}(\boldsymbol{\phi}\cdot\boldsymbol{n}, Q_{k-1}^Fv)_{F} \\
&=h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2.
\end{align*}
By the norm equivalence \eqref{eq:Vknormequivalence}, we get
\begin{equation}\label{eq:20220204}
\|\nabla v\|_{0,K}^{2}\lesssim h_K^{-2}\|Q_{k-2}^Kv\|_{0,K}^2+\sum_{F\in\mathcal F(K)}h_K^{-1}\|Q_{k-1}^Fv\|_{0,F}^2= (\boldsymbol{\phi}, \nabla v)_K.
\end{equation}

@@

\subsection{Discrete method}
Define the global nonconforming virtual element space
\begin{align*}
V_h&:=\{v_h\in L^2(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h, \textrm{  } \\
&\qquad\; \textrm{DoFs \eqref{eq:vemdof1} are single-valued for $F\in\mathcal F_h$, and vanish for $F\in \mathcal F_h^{\partial}$}\}.
\end{align*}
We have the discrete Poincar\'e inequality \cite{Brenner2003}%(cf. \cite[(4.16)]{ChenHuang2020ncvem})
\begin{equation}\label{eq:vempoincareineqlty}
\|v_h\|_0\XH{\leq C_p} |v_h|_{1,h} \quad\forall~v_h\in V_h,
\end{equation}
\XH{where the constant $C_p$ is independent of the mesh size.}
Hence $|\cdot|_{1,h}$ is indeed a norm for $V_h$.
% Introduce discrete spaces
% \begin{align*}
% \mathbb{V}_{h,k-1}^{\rm div}&:=\{\boldsymbol{\phi}_h\in \boldsymbol{L}^2(\Omega;\mathbb R^d): \boldsymbol{\phi}_h|_K\in \mathbb{V}_{k-1}^{\rm div}(K) \textrm{ for each } K\in\mathcal T_h\}, \\
% \mathbb P_l(\mathcal T_h)&:=\{q_h\in L^2(\Omega): q_h|_K\in \mathbb P_l(K) \textrm{ for each } K\in\mathcal T_h\}
% \end{align*}
% with non-negative integer $l$.
% For $\boldsymbol{\phi}\in\boldsymbol{L}^2(\Omega;\mathbb R^d)$, let $Q_h^{\div}\boldsymbol{\phi}\in\mathbb{V}_{h,k-1}^{\rm div}$ be determined by $(Q_h^{\div}\boldsymbol{\phi})|_K=Q_K^{\div}(\boldsymbol{\phi}|_K)$ for each $K\in\mathcal T_h$. For $v\in L^2(\Omega)$, let $Q_h^lv\in \mathbb P_l(\mathcal T_h)$ be determined by $(Q_h^{l}v)|_K=Q_{l}^K(v|_K)$ for each $K\in\mathcal T_h$. For simplicity, the vector version of $Q_h^l$ is still denoted by $Q_h^l$. And we abbreviate $Q_h^k$ as $Q_h$ if $l=k$.

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:vem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation}
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
\]

@@

Based on the weak formulation \eqref{eq:ellipitc2ndproblemweakform}, we propose a virtual element method \XH{without extrinsic stabilization} for problem \eqref{eq:ellipitc2ndproblem} as follows: find $u_h\in V_h$ such that
\begin{equation}\label{eq:cfmvem}
a_h(u_h, v_h)=(f, Q_hv_h)\quad\forall~v_h\in V_h,
\end{equation} 
where the discrete bilinear form 
\[
a_h(u_h, v_h):=(Q_{h,k}^{\div}\nabla u_h, Q_{h,k}^{\div}\nabla v_h)+\alpha(Q_hu_h, Q_hv_h).
\]
The VEM \eqref{eq:cfmvem} is uni-solvent.
